---
title: "Errata for *How Experiments Help Campaigns Persuade Voters*"
format:
  pdf:
    output-file: hewitt_etal_2024_errata.pdf
    toc: false
    number-sections: false
    geometry: margin=1in
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
here::i_am("errata.qmd")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

published_claims <- read_csv(
  here::here("ground_truth", "published_claims.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)
published_maintext <- read_csv(
  here::here("ground_truth", "published_maintext_tables.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)
published_appendix <- read_csv(
  here::here("ground_truth", "published_appendix_values.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)
estimates <- read_csv(here::here("maintained", "output",
                                 "metaregression_estimates.csv"),
                      show_col_types = FALSE)
main_claims <- read_csv(here::here("maintained", "output", "text_main_claims.csv"),
                        show_col_types = FALSE)
table_1_cells <- read_csv(here::here("maintained", "output",
                                     "table_1_studies_summary_cells.csv"),
                          show_col_types = FALSE)

quantity <- function(name) {
  row <- main_claims |> filter(.data$quantity == .env$name)
  stopifnot(nrow(row) == 1)
  row$value
}

published_cell <- function(float_id, key, quantity_id) {
  row <- bind_rows(published_maintext, published_appendix) |>
    filter(float == float_id, row_key == key, quantity == quantity_id)
  stopifnot(nrow(row) == 1)
  row$value_paper
}

table_1_value <- function(dataset_name, quantity_id) {
  row <- table_1_cells |>
    filter(dataset == dataset_name, quantity == quantity_id)
  stopifnot(nrow(row) == 1)
  row$value
}

omnibus <- estimates |>
  filter(metareg_name == "All primary", specification == "standard",
         weighting == "unweighted", term == "r2_comparison")

dichotomized_mu <- estimates |>
  filter(metareg_group == "overall", specification == "no_moderators",
         weighting == "unweighted", term == "intercept",
         outcome == "votechoice_dichotomized")

tau_2018 <- quantity("tau_votechoice_2018")
r2_votechoice_max <- max(omnibus$estimate[omnibus$outcome == "votechoice"])
mu_downballot <- dichotomized_mu$estimate[dichotomized_mu$dataset == "2020 Downballot"]
icc_pushy <- quantity("icc_pushy_single_rater")
```

```{r entries}
# THE ERRATA SPINE. Every correction this note makes is defined once, in the tibble
# below, and the document is rendered from it. Nothing is retyped downstream: the
# emitters read the fields and supply only headings and punctuation. The same spine is
# written to errata_entries.csv at the foot of this file, so a later edition of the
# article reads it rather than keeping a second hand-typed copy of the same corrections,
# which is how two copies of a correction drift apart.
#
# [[...]] marks the span that changes, and it is the only markup permitted in the
# published and corrected fields. Each renderer resolves it its own way: bold here, a
# \was{} macro in an edition. LaTeX math, quotation marks and everything else stay
# literal text.
#
# Numbering is APPEND-ONLY. An entry number can already have been cited, so a later
# finding is added at the end; existing entries are never reordered, renumbered, merged
# or split.
#
# Every corrected value, and every published value the transcription records, is computed
# at render time from the pipeline outputs read in `setup`. None is a literal, so this
# note cannot state a number the reanalysis no longer produces.
#
# Entry 1 corrects one misstatement made in two separate sentences of the article. It is
# a single entry: its two passages, their two locations and its two paragraphs of prose
# are joined inside the fields with `part_sep` and split back out by that entry's emitter.
part_sep <- "\n\n@@\n\n"

entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note,

  1, "quantity", "pipeline", "full",
  "The 2018 standard deviation of true effects on vote choice",
  paste0("p. 2", part_sep, "p. 10"),
  paste0(
    "In addition, we find that common theories [...] our meta-analytic results indicate ",
    "that the standard deviation of the distribution of true treatment effects were ",
    "[[1.5]] points, 0.5 points, and 0.3 points, respectively, or roughly about half the ",
    "size of the average effect.",
    part_sep,
    "In 2018, the estimated standard deviation of the true treatment effects ",
    "($\\hat\\tau$) was [[1.5]] points, but in both the downballot and presidential races ",
    "in 2020, the standard deviations were smaller, at 0.5 and 0.3 percentage points."),
  paste0(
    str_glue(
      "our meta-analytic results indicate that the standard deviation of the ",
      "distribution of true treatment effects were [[{sprintf('%.1f', tau_2018)}]] ",
      "points, 0.5 points, and 0.3 points, respectively, or roughly about half the size ",
      "of the average effect."),
    part_sep,
    str_glue(
      "In 2018, the estimated standard deviation of the true treatment effects ",
      "($\\hat\\tau$) was [[{sprintf('%.1f', tau_2018)}]] points, but in both the ",
      "downballot and presidential races in 2020, the standard deviations were smaller, ",
      "at 0.5 and 0.3 percentage points.")),
  paste0(
    str_glue(
      "The article gives this quantity as 1.5 points in two places. Table 2 gives it as ",
      "{published_cell('table_2', 'Vote choice | 2018', 'tau_no_moderators')}."),
    part_sep,
    str_glue(
      "The reanalysis returns {sprintf('%.2f', tau_2018)}, which is what Table 2 prints ",
      "and which rounds to {sprintf('%.1f', tau_2018)}. The two 2020 figures are correct ",
      "as published.")),

  2, "quantity", "pipeline", "full",
  "The range of R-squared values for vote choice",
  "p. 11",
  paste0(
    "When we include all primary hypotheses in one meta-regression, the adjusted $R^2$ ",
    "values range between 0.12 and 0.34 for favorability and between 0 and [[0.32]] for ",
    "vote choice."),
  str_glue(
    "When we include all primary hypotheses in one meta-regression, the adjusted $R^2$ ",
    "values range between 0.12 and 0.34 for favorability and between 0 and ",
    "[[{sprintf('%.2f', r2_votechoice_max)}]] for vote choice."),
  str_glue(
    "The three vote choice cells of the \"$\\hat R^2$ (all vs. control)\" row of ",
    "Dataverse Appendix Table DA28 are ",
    "{published_cell('table_da28', 'Vote choice | R2 all vs control | 2018', 'value')}, ",
    "{published_cell('table_da28', 'Vote choice | R2 all vs control | 2020D', 'value')} ",
    "and ",
    "{published_cell('table_da28', 'Vote choice | R2 all vs control | 2020P', 'value')}. ",
    "The sentence takes the 2018 figure as the upper end of the range where the 2020 ",
    "downballot figure is larger. The favorability range in the same sentence is ",
    "correct."),

  3, "quantity", "pipeline", "full",
  "The average survey treatment effect quoted in Appendix C.1",
  "Online Appendix, p. OA20",
  paste0(
    "Compared these values with the average survey treatment effects $\\mu$ from Table ",
    "OA2, we calculate the survey-to-field conversion factor to be approximately 100 ",
    "(= 0.015 / [[1.53]]) based on the 2020 Downballot dataset."),
  str_glue(
    "Compared these values with the average survey treatment effects $\\mu$ from Table ",
    "OA2, we calculate the survey-to-field conversion factor to be approximately 100 ",
    "(= 0.015 / [[{sprintf('%.2f', mu_downballot)}]]) based on the 2020 Downballot ",
    "dataset."),
  str_glue(
    "Table OA2 gives {published_cell('table_oa2', '2020 Downballot', 'mu')} for the 2020 ",
    "downballot mean effect on the dichotomised vote choice scale, which the reanalysis ",
    "returns exactly. The conversion factor is unchanged at approximately 100."),

  4, "quantity", "pipeline", "brief",
  "The last 2020 downballot study in Table 1",
  "",
  str_glue(
    "The \"Last study\" cell of Table 1's 2020 downballot row reads ",
    "[[{published_cell('table_1', '2020 Downballot', 'last_study')}]]."),
  str_glue("[[{table_1_value('2020 Downballot', 'last_study')}]]."),
  str_glue(
    "The changed artifact is that cell alone; every other cell of Table 1 reproduces. ",
    "The deposited code reads the last row of the study file rather than the latest ",
    "date, and the file is not in date order: the study dated ",
    "{table_1_value('2020 Downballot', 'last_in_file')} is the last row, and the study ",
    "dated {table_1_value('2020 Downballot', 'last_study')} is the last study."),

  5, "quantity", "pipeline", "full",
  "The reliability of the pushiness rating",
  "p. 8",
  paste0(
    "Research assistants were highly consistent in their ratings of the most explicit ",
    "features such as the race and gender of the primary messenger (single-rater ICC ",
    "$>$ 0.8), but less consistent in their ratings of the most subjective ",
    "characteristics, such as how \"pushy\" the ad was (single-rater ICC = [[0.23]])."),
  str_glue(
    "Research assistants were highly consistent in their ratings of the most explicit ",
    "features such as the race and gender of the primary messenger (single-rater ICC ",
    "$>$ 0.8), but less consistent in their ratings of the most subjective ",
    "characteristics, such as how \"pushy\" the ad was (single-rater ICC = ",
    "[[{sprintf('%.2f', icc_pushy)}]])."),
  str_glue(
    "A rounding error rather than a different quantity: the deposited single-rater ",
    "intraclass correlation for the pushiness item is {sprintf('%.4f', icc_pushy)}. The ",
    "claim about the messenger items in the same sentence holds.")
) |>
  mutate(across(c(title, location, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. An edition resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")

# The shape entries 2, 3 and 5 share: heading, the published passage as a blockquote with
# its location, the corrected sentence, then the explanatory paragraph. A heading is only
# a heading when a blank line precedes it, hence the leading newlines.
emit_full <- function(e) {
  cat("\n\n## ", e$entry, ". ", e$title,
      "\n\n> ", bold(e$published), " (", e$location, ")",
      "\n\nCorrected: ", bold(e$corrected),
      "\n\n", e$note, "\n", sep = "")
}

# The count below is spelled out in prose, so it is derived rather than typed.
n_word <- c("One", "Two", "Three", "Four", "Five", "Six", "Seven", "Eight", "Nine", "Ten")
```

`r n_word[nrow(entries)]` corrections to Hewitt, Broockman, Coppock, Tappin, Slezak, Coffman, Lubin and Hamidian, "How Experiments Help Campaigns Persuade Voters: Evidence from a Large Archive of Campaigns' Own Experiments," *American Political Science Review* (2024), `10.1017/S0003055423001387`.

None of them changes a conclusion of the article. In each case the corrected figure is the one the article's own tables already print, recomputed here from the deposited data at Harvard Dataverse (`10.7910/DVN/LBPSSV`). Corrected values on the percentage point scale are given at one decimal place throughout; the reliability coefficient in entry 5 keeps the article's own two decimals, since one would erase the correction. The changed token is bold on both sides of each entry.

```{r}
#| label: entry-1
#| results: asis
e <- entries |> filter(entry == 1)
pub <- str_split_1(e$published, fixed(part_sep))
cor <- str_split_1(e$corrected, fixed(part_sep))
loc <- str_split_1(e$location, fixed(part_sep))
nte <- str_split_1(e$note, fixed(part_sep))
cat("\n\n## ", e$entry, ". ", e$title,
    "\n\n", nte[1],
    "\n\n> ", bold(pub[1]), " (", loc[1], ")",
    "\n\nCorrected: ", bold(cor[1]),
    "\n\n> ", bold(pub[2]), " (", loc[2], ")",
    "\n\nCorrected: ", bold(cor[2]),
    "\n\n", nte[2], "\n", sep = "")
```

```{r}
#| label: entries-2-3
#| results: asis
walk(c(2, 3), function(i) emit_full(entries |> filter(entry == i)))
```

```{r}
#| label: entry-4
#| results: asis
e <- entries |> filter(entry == 4)
cat("\n\n## ", e$entry, ". ", e$title,
    "\n\n", bold(e$published),
    "\n\nCorrected: ", bold(e$corrected),
    "\n\n", e$note, "\n", sep = "")
```

```{r}
#| label: entry-5
#| results: asis
emit_full(entries |> filter(entry == 5))
```

```{r}
#| label: emit-spine
write_csv(entries, here::here("errata_entries.csv"))
```
